\documentclass[11pt]{article}
\usepackage{graphicx} % Required for inserting images
\setlength{\parindent}{0pt}
\usepackage{enumitem}
\usepackage[utf8]{inputenc} 
\usepackage[T1]{fontenc}
\usepackage[brazil]{babel}
\usepackage{lipsum}
\usepackage[left=1.06cm,top=1.7cm,right=1.06cm,bottom=0.49cm]{geometry}

\begin{document}
\begin{center}
    \textbf{Saswat Parasar Behera}\\ 
    \hrulefill
\end{center}

\begin{center}
   Bhubaneswar, Odisha \textbullet \ github.com/majorbruteforce \textbullet \ b122103@iiit-bh.ac.in
\end{center}

\vspace{0.5pt}

\begin{center}
    \textbf{Education}
\end{center}
\textbf{International Institute of Information and Technology, Bhubaneswar} \hfill Bhubaneswar, Odisha

B.Tech, Computer Science and Engineering . GPA 7.39 \hfill 2022-2026 

\vspace{1pt}

\textbf{DAV Public School, Chandrasekharpur} \hfill	Bhubaneswar, Odisha

Percentage: 95.6 \hfill 2019-2021

\vspace{1pt}

\textbf{Loyola School, Bhubaneswar} \hfill	Bhubaneswar, Odisha

Percentage: 93.3 \hfill 2018-2019


\vspace{5pt}

\begin{center}
    \textbf{Experience}
\end{center}


\textbf{Runners-up in D3 Inter-college Hackathon}

\textit{Team Leader}
\vspace{5pt}
Created a \textbf{real time multi user text-editor} with team.
\begin{itemize}[noitemsep]
    \item Worked on the backend; created routes, controllers for server database interaction;
    refactored web socket room creation logic; facilitated on-demand spin up of docker containers to run code in isolation. 
    \item Unit tested using jest; deployed code to vercel; facilitated connection to docker over local network
\end{itemize}

\vspace{5pt}

\textbf{Programming Society, IIIT Bhubaneswar } 

\textit{Associate, Web Development}

\vspace{3pt}
\begin{itemize}[noitemsep]
    \item Engaged in conducting informative sessions on popular technologies fro undergraduate students; offered assistance.
\end{itemize}

\vspace{5pt}

\begin{center}
    \textbf{Projects}
\end{center}

\textbf{Tunescape} \textit{Node.js, Express.js, MongoDB, AWS}

A Community Music Stream-Sharing Platform based on the cloud allowing users to share and listen to music online.

\begin{itemize}[noitemsep]
    
    \item Created the server using \textbf{Node.js} and \textbf{Express.js} to handle routing, database CRUD operations, middleware to authenticate users/admin
    \item Wrote logic to store uploaded music and image files to \textbf{AWS S3 Bucket} using \textbf{multer}
    \item Distributed the files using \textbf{AWS Cloudfront} as the CDN to facilitate on-demand low latency streaming.
\end{itemize}
\textbf{Fuse: Collaborative Code Editor} \textit{Node.js, Express.js, Socket.io, WebRTC, docker}

A Realtime Interactive Code Editor allowing users to collaborate and code online, make changes and run code on the cloud.

\begin{itemize}[noitemsep]
    
    \item Worked on the backend using \textbf{Node} to create the server, interact with \textbf{MongoDB}, \textbf{Socket.io} to create websocket connections.
    \item Wrote logic to run \textbf{Docker} containers to run the code in isolated environments.
    \item Deployed platform code to Vercel and tested docker logic on \textbf{AWS EC2}
\end{itemize}
\textbf{Kiwi: CLI Web Crawler} \textit{Node.js}

A minimalist web crawler CLI Tool.

\begin{itemize}[noitemsep]
    
    \item Created using \textbf{Node} to scrap web markup and crawl links recursively.
    \item Created configurations to run globally on any machine.
\end{itemize}

\begin{center}
    \textbf{Skills \& Interests}
\end{center}

\textbf{Languages:} C, C++, Typescript, Javascript, Python, Golang

\textbf{Frontend:} HTML, CSS, EJS, Tailwind

\textbf{Backend:} Node.js, Docker, Redis, Mux

\textbf{Database:} MongoDB, Mongo Change Streams

\textbf{Cloud:} AWS (EC2, Cloudfront, S3), Azure




\end{document}
